\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix}

% to be able to draw some self-contained figs
\usepackage{tikz}
\usepackage{amsmath}

% inlined bib file
\usepackage{filecontents}
\usepackage{booktabs} % 用于三线表 (\toprule, \midrule, \bottomrule)
\usepackage{multirow} % 用于合并行
\usepackage{array}    % 用于更好的列控制
\usepackage{caption}  % 用于美化标题
\usepackage{graphicx}   % 用于插入图片
\usepackage{subcaption} % 用于创建子图网格
\usepackage{makecell}
\usepackage{threeparttable}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{tabularx} 
\usepackage{booktabs} 
\usepackage{amssymb} % 提供 \checkmark
\newcommand{\OurWork}{Our work}


\usepackage[capitalize]{cleveref}
\newcommand{\qh}[1]{\textcolor{blue}{[Qinhong: #1]}}
\newcommand{\hr}[1]{\textcolor{green}{[Haoran: #1]}}
\newcommand{\ly}[1]{\textcolor{red}{[Yan: #1]}}
\newcommand{\alias}{\texttt{InjectEave}}



\begin{document}
%-------------------------------------------------------------------------------

%don't want date printed
\date{}

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Injected and Leaked: Actively Inducing Side-channel Leakage Using Electromagnetic Injection And Hardware Non-Linearity}

%for single author (just remove % characters)
\author{
{\rm Your N.\ Here}\\
Your Institution
\and
{\rm Second Name}\\
Second Institution
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
} % end author

\maketitle

%\input{outline}

\input{sections/0-abstract}

\input{sections/1-Introduction}

\input{sections/2-Background}

\input{sections/3-Injection-induced Electromagnetic Side-channel Leakage}

\input{sections/4-Eavesdropping Design}

\input{sections/5-Evaluation in a Laboratory Setting_new}

\input{sections/6-Audio Eavesdropping in the Wild_new}

\input{sections/7-Discussion.tex}

\input{sections/8-Conclusion.tex}



%-------------------------------------------------------------------------------
\section*{Acknowledgments}
%-------------------------------------------------------------------------------

The USENIX latex style is old and very tired, which is why
there's no \textbackslash{}acks command for you to use when
acknowledging. Sorry.

\textbf{Do not include any acknowledgements in your submission which may deanonymize you (e.g., because of specific affiliations or grants you acknowledge)}

%-------------------------------------------------------------------------------
% optional clearing of the page
\cleardoublepage
\appendix
\section*{Ethical  Considerations}
% \textbf{Human Subjects and Privacy Protection.} Given that our research involves the recovery of human speech and the inference of user activities through smart home devices, we implemented strict protocols to safeguard privacy and ethical standards. All experiments involving audio recording, including the "in-the-wild" scenarios simulating hotel and meeting room environments, were conducted exclusively with the authors and volunteer colleagues who provided explicit, informed consent. We ensured that no unsuspecting individuals were targeted, and no private conversations from the public were intercepted or recorded. 

% Furthermore, the collected speech data was utilized solely for the purpose of training the denoising model and evaluating attack performance. We rigorously excluded any Personally Identifiable Information (PII) beyond the voice biometric itself, and all data was stored securely with access restricted to the research team. As this study focuses on systemic hardware vulnerabilities rather than behavioral research, and participation was limited to the research team, the study falls outside the requirements for formal Institutional Review Board (IRB) approval, though we strictly adhered to the ethical principles outlined in the Belmont Report.

% \textbf{Regulatory Compliance and Operational Safety.} The deployment of active electromagnetic injection techniques necessitates rigorous adherence to safety and regulatory standards to prevent unintended interference. All injection experiments were conducted within controlled laboratory environments. We strictly monitored transmission frequencies and power levels to ensure compliance with local radio frequency regulations, keeping transmission power to the minimum necessary for proof-of-concept validation. Specifically, the "active manipulation" experiments targeting landline phones were performed on localized, private circuits that were physically disconnected from the Public Switched Telephone Network (PSTN) to eliminate any risk of disrupting critical infrastructure.

% \textbf{Responsible Disclosure and Defense Against Misuse.} We identified significant physical-layer vulnerabilities in 15 Commercial Off-The-Shelf (COTS) devices from various manufacturers. In accordance with responsible disclosure practices, we have initiated communication with the affected vendors, providing them with detailed findings regarding the susceptibility of unshielded analog interfaces to injection-induced leakage. We have also shared specific hardware-level mitigation strategies, such as the necessity for shielding post-decryption analog lines and incorporating filters to suppress high-frequency carrier coupling. We recognize that the "Injection-Induced Side Channel" and the "Listen-Decide-Act" kill chain demonstrated in this work pose significant risks if misused for espionage or fraud. Consequently, to minimize the risk of malicious exploitation, we are releasing only a subset of the raw and received audio samples from the experiments. We explicitly withhold the precise modulation profiles for specific commercial devices. 

% \textbf{Risk-Benefit Analysis.} Despite the inherent risks associated with disclosing physical-layer vulnerabilities, we believe that publishing this work is imperative. Current security models largely operate under the assumption that analog interfaces are adequately secured by upstream digital encryption or physical air-gaps. This creates a defensive asymmetry where attackers can exploit fundamental hardware non-linearities while defenders lack the models to assess these risks. By demonstrating that hardware non-linearity can effectively bridge these gaps, we aim to correct this asymmetry and compel the hardware industry to re-evaluate and strengthen physical layer security standards for analog components.

\noindent\textbf{Human Subjects and Behavioral Privacy.}
Our research involves sensitive data recovery, ranging from human speech to behavioral patterns inferred from smart home devices. We adhered to strict ethical protocols to safeguard participant rights. All experiments, including the "in-the-wild" scenarios, were conducted exclusively with the authors and volunteer colleagues who provided explicit, informed consent.
Crucially, our privacy protection extended beyond voice biometrics to \textit{behavioral metadata}. As demonstrated in our attacks on smart fans and lamps, device states can proxy personal habits. We treated these behavioral signatures with the same rigor as Personally Identifiable Information (PII), ensuring no data retention beyond the immediate evaluation needs.
Furthermore, given the use of active EM injection near the human body, we strictly monitored transmission power. All injection levels were maintained well below the specific absorption rate (SAR) limits for general population exposure to ensure the physical safety of our volunteers.

\noindent\textbf{Responsible Disclosure of Unpatchable Hardware.}
We identified significant physical-layer vulnerabilities in 11 Commercial Off-The-Shelf (COTS) devices. We have responsibly disclosed our findings to the affected vendors, providing detailed analysis of the analog interface vulnerabilities.
% However, a unique ethical dilemma arises from the nature of this threat: unlike software bugs, the exploited hardware non-linearities cannot be remediated via Over-the-Air (OTA) firmware updates. This creates a prolonged window of vulnerability for existing deployed hardware. 
In our disclosure, we emphasized future design standards—such as shielding post-decryption analog lines and integrating EMI filters—while deliberately withholding the precise modulation parameters and optimal carrier frequencies from this publication to minimize the immediate risk of weaponization against current users.

\noindent\textbf{Risks of Active Manipulation and Generative AI.}
Our demonstration of the "Listen-Decide-Act" kill chain introduces a critical ethical dimension: the fusion of physical-layer injection with voice cloning. This capability elevates the threat from passive confidentiality loss to active integrity violation, enabling identity impersonation.
Recognizing the severe implications of combining EM injection with Deepfake technology, we restricted all active manipulation experiments to localized, private circuits physically disconnected from the Public Switched Telephone Network (PSTN). This air-gapped setup ensured that no fraudulent signals or synthesized voice traffic could enter public telecommunication infrastructure.

\noindent\textbf{Operational Safety in Non-Line-of-Sight Scenarios.}
Conducting active injection attacks in semi-public spaces carries the risk of collateral interference. To mitigate this, we employed strict spectrum monitoring prior to and during experiments to ensure our injection frequencies did not disrupt bystanders' devices or critical wireless services. The experiments were time-limited and performed only when the immediate electromagnetic environment was controlled to prevent Denial-of-Service (DoS) effects on non-target electronics.

\noindent\textbf{Risk-Benefit Analysis.}
Despite the inherent risks associated with disclosing unpatchable physical-layer vulnerabilities, we believe publishing this work is imperative to correct a defensive asymmetry. Current security models largely assume analog interfaces are secured by upstream digital encryption. By demonstrating that hardware non-linearity renders these assumptions obsolete, we aim to compel the hardware industry to adopt rigorous physical-layer hardening standards, ensuring that the "last mile" of analog interaction is as secure as the digital pipeline.

\cleardoublepage

\section*{Open Science}
\textbf{Within up to one page, this appendix must list all artifacts necessary to evaluate the contribution of the paper and make clear how the review committees can access each artifact. This appendix must have exactly this title, otherwise you will risk desk rejection. }

\hr{Zenodo, website}

%impact测量结果表格，case study1 六句对话， case study2 回答句子，合成句子 denoise 代码


% optional clearing of the page
\cleardoublepage
\bibliographystyle{plain}
\bibliography{refs}

\cleardoublepage
\input{sections/9-Appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%  LocalWords:  endnotes includegraphics fread ptr nobj noindent
%%  LocalWords:  pdflatex acks
